Meta-analysis Manuscript Wrangling

### 2021-07-15 shared analysis files /manuscript_datavis_22jun21.Rmd
model troubleshooting and figure generation

                                            "feeding rate", ,

@@

count(dat_full_var_ES, metric)
```
# Motivation and Hypotheses

@@

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp +environment, 
               random = ~1 |  study_id/ response_id,
                 method="REML") 
acclimation_model
```

@@

full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level +environment, 
               random = list(~1 | study_id/ response_id),
                 method="REML") 
full_var_model

@@

@@

f

@@

```{r}
g <- dat_full_var_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-2.6,1.7)+
  coord_flip()+
  ggtitle("ASSAY")

h <- dat_acclim_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-2.6,1.7)+
  coord_flip()+
  ggtitle("ACCLIMATION")

h / g
```

@@

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "Mean temperature (°C)",
       y ="SMD",
       fill = "Temperature fluctuation range (°C)")+
  theme(legend.position="bottom")

ggplot(normalized_var, aes(y=yi, x=mean_temp_constant, fill=mean_temp_constant))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and mean temperature")+
  labs(x = "Mean temperature (°C)",
       y ="SMD",
       fill = "Mean temperature (°C)")+
  theme(legend.position="bottom")
```

## Funnel plot of acclimation data 
````{r, echo=FALSE}
funnel(dummy_acclim, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)
```
## Funnel plot of non-linear averaging + acclimation data 
````{r, echo=FALSE}
funnel(dummy_var, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)
```

>>>>

                                            "feeding rate",

@@

```
# Motivation and Hypotheses

@@

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=normalized_acclim, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp +environment +metric, 
               random = ~1 |  study_id/response_id,
                 method="REML") 
acclimation_model
```

@@

full_var_model <-rma.mv(yi, vi, data=normalized_var, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size  +environment +org_level +metric, 
               random = ~1 | study_id/response_id,
                 method="REML") 
full_var_model

@@

```{r}
#devtools::install_github("MathiasHarrer/dmetar")
library(dmetar)
res <- var.comp(full_var_model)
plot(res)

res_acclim <- var.comp(acclimation_model)
plot(res_acclim)

@@

@@

```{r}
h <- dat_full_var_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-3,1.7)+
  coord_flip()+
  ggtitle("ASSAY")

i <- dat_acclim_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-3,1.7)+
  coord_flip()+
  ggtitle("ACCLIMATION")

i / h

h <- dat_full_var_ES %>%
  group_by(metric)%>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  ggplot(aes(x=metric, y=mean_yi, fill = mean_yi > 0))+
  geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  geom_point(size = 4, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  xlab("Metric")+
  ylim(-3,1.7)+
  coord_flip()+
  ggtitle("ASSAY")

i <- normalized_acclim %>%
  ggplot(aes(x=yi, y=mean_temp_reared,size = flux_range))+
  #geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  #geom_boxplot(aes(fill = yi > 0))+
  geom_point(aes(fill = yi > 0), alpha=0.8, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  coord_flip()+
  ggtitle("ACCLIMATION")+
  facet_wrap(~metric)

j <- normalized_var %>%
  ggplot(aes(x=yi, y=mean_temp_constant, size=flux_range))+
  #geom_errorbar(aes(ymin=mean_yi-mean_vi, ymax=mean_yi+mean_vi), width=.2)+
  #geom_boxplot(aes(fill = yi > 0))+
  geom_point(aes(fill = yi > 0), alpha=0.8, show.legend = FALSE, pch=21,colour="black")+
  scale_fill_viridis(discrete = TRUE)+
  coord_flip()+
  ggtitle("ASSAY")+
  facet_wrap(~metric)

i + j

@@

ggplot(normalized_var, aes(y=yi, fill=mean_temp_constant, x=flux_range))+
  geom_jitter(alpha = 0.5, pch=21,size=1, width = 0.3, height = 0.7)+
  geom_line(y=0, linetype = "dashed")+
  geom_errorbar(data=mean_var, aes(ymin=yi-vi, ymax=yi+vi), size=.7, width=.4, color = "black")+
  geom_jitter(data = mean_var, size=4, pch=21, colour="black")+
  theme_bw()+
  scale_fill_viridis()+
  ggtitle("Non-linear averaging + acclimation and fluctuation range")+
  labs(x = "flux range",
       y ="SMD",
       fill = "mean temp")+
  theme(legend.position="bottom")+ 
  facet_wrap(~mean_temp_constant)
```

## Funnel plot of acclimation data 
````{r, echo=FALSE}
funnel(acclimation_model, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)

par(mfrow=c(2,2))

### draw funnel plots
funnel(dummy_acclim, main="Standard Error")
funnel(dummy_acclim, yaxis="vi", main="Sampling Variance")
funnel(dummy_acclim, yaxis="seinv", main="Inverse Standard Error")
funnel(dummy_acclim, yaxis="vinv", main="Inverse Sampling Variance")

funnel(dummy_var, main="Standard Error")
funnel(dummy_var, yaxis="vi", main="Sampling Variance")
funnel(dummy_var, yaxis="seinv", main="Inverse Standard Error")
funnel(dummy_var, yaxis="vinv", main="Inverse Sampling Variance")

ggplot(normalized_acclim, aes(y=yi, x=vi))+
  geom_point()

ggplot(normalized_var, aes(y=yi, x=vi))+
  geom_point()

```
## Funnel plot of non-linear averaging + acclimation data 
````{r, echo=FALSE}
funnel(full_var_model, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)
```
